---
title: "WASPAS in a nutshell"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{WASPAS in a nutshell}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(waspasR)
```
## Abstract

Reliable data and formal mathematical processes are valuable resources for decision-making processes. There are many scientific methods proposed by studies carried out in the field of Operational Research [OR] to support decision makers. The complexity of the sets of variables that must be considered in each decision-making increases uncertainties. Managers looking for assertiveness in communicating their decisions find these methods an important tool for justifying the decisions taken. However, the main obstacle to the use of these scientific resources is their intrinsic complexity. Many managers have an understandable difficulty dealing with the mathematical formalism of the long and detailed formulas that document the algorithms implementation of decision-making methods based on multiple criteria. This Completion of Course Work [CCW] proposes to offer a public mechanism, available on the internet, so that any decision maker can use the proposed method as a support tool, without needing knowledge of programming or the heavy computation used in the calculations. Another contribution of this CCW to society was the publication of a package in the community of users of the R language, Comprehensive R Archive Network [CRAN]. We also submitted a scientific article to the journal of whatever, which is in the approval process. The “Weighted Aggregated Sum Product Assessment [WASPAS]” method, proposed by Zavadskas et al. (2012), was chosen for this implementation. WASPAS, according to Baykasoğlu and Gölcük (2020) is relatively new and has had increasing visibility in the related technical literature.
Keywords: CRAN; Shiny; Multicriteria; Decision Theory, Operations Research.
