---
title: "WASPAS in a nutshell"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{WASPAS in a nutshell}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(waspasR)
```

## waspasR motivation

Reliable data and formal mathematical processes are valuable resources for decision-making processes. There are many scientific methods proposed by studies carried out in the field of Operational Research [OR] to support decision makers. The complexity of the sets of variables that must be considered in each decision-making increases uncertainties. Managers looking for assertiveness in communicating their decisions find these methods an important tool for justifying the decisions taken. However, the main obstacle to the use of these scientific resources is their intrinsic complexity. Many managers have an understandable difficulty dealing with the mathematical formalism of the long and detailed formulas that document the algorithms implementation of decision-making methods based on multiple criteria. The **waspasR** package proposes to offer a set of functions to easily create R applications that implement a suitable MCDM (Multiple Criteria Decision Making) method to determine the optimal alternative in a MCDM process. It is the "Weighted Aggregated Sum Product Assessment [WASPAS]" method, proposed by Zavadskas et al. (2012) \<<doi:10.5755/j01.eee.122.6.1810>\>

Since WASPAS is composed by other two underlying methods WSM (Weighted Sum Model) and WPS (Weighted Product Model) these are also covered by **waspasR** package.

For application in complex decision-making processes, where large sets of alternatives and criteria must be considered, MCDM systems can be successfully applied. It was proved that the accuracy of two methods used together is greater than the accuracy of each of the methods applied separately. WASPAS implements this principle by aggregating the Weighted Sum Model [WSM] and Weighted Product Model [WPM] methods. WSM is one of the most known and used MCDM methods applied to problems of this category. WPM is a variation that uses the weight-value exponentiation product instead of the sum of multiplication.
